Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches

### 2022-11-30 paper.tex
Overleaf commit, converted the paper to two columns format.
fixed IC figure and it's reference

\documentclass[review]{elsarticle}
\usepackage{etoolbox}
\usepackage{lineno,hyperref}
\let\oldbibliography\thebibliography
\renewcommand{\thebibliography}[1]{%
  \oldbibliography{#1}%
  \setlength{\itemsep}{0pt}%
}

@@

%\newcommand{\mycaption}[1]{\stepcounter{figure}\raisebox{-7pt}
%  {\footnotesize Fig. \thefigure.\hspace{3pt} #1}}

@@

% % %% Group authors per affiliation:
% % %% or include affiliations in footnotes:
\author[add]{Gökhan Göktürk}
% \ead{gokhan.gokturk@sabanciuniv.edu}

\author[add]{Kamer Kaya}
% \ead{kaya@sabanciuniv.edu}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% However, these simulation-based, greedy algorithms provide the best possible approximation guarantees. Therefore they are considered as the gold standard for IM.

@@

% \begin{figure}[!ht] 
%     \centering
%   \subfloat[\small{IC}\label{fig:ic}]{%
%        \includegraphics[width=0.4\linewidth]{images/ic.pdf}}
%   \subfloat[\small{WC}\label{fig:wc}]{%
%         \includegraphics[width=0.4\linewidth]{images/wc.pdf}}
%     \\% IMAGES HERE
%   \caption{\small{\protect\subref{fig:ic} 
% The directed graph $G = (V, E)$ for IC with independent diffusion probabilities. 
% \protect\subref{fig:wc}
% The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma^-_G(v)|$ for each vertex $v \in V$.% \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.} 
%   }}
%   %\label{fig_ic_model} 
%   \label{fig:xx} 
% \end{figure}
% \FloatBarrier
% \begin{itemize}[leftmargin=*]
% \item The {\bf Independent Cascade} model \fixme{works in rounds and activates} a vertex $v$ in the current round if one of $v$'s \fixme{incoming edges $(u, v)$ is used during the diffusion} round, \fixme{which happens with the activation probability $w_{u, v}$, given that $u$ has already been} influenced \fixme{in the previous rounds. The activation probabilities are independent (from each other and previous activations)} in the {\em independent cascade} model, which we focus on in this paper. A toy graph with activation probabilities on the edges is shown in Figure~\ref{fig:ic}.
% In theory, there can exist parallel and independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing.

>>>>

\documentclass[final,5p,times,twocolumn]{elsarticle}
% \documentclass[review]{elsarticle}
\usepackage{etoolbox}
\usepackage{lineno,hyperref}
\let\oldbibliography\thebibliography
\renewcommand{\thebibliography}[1]{%
  \oldbibliography{#1}%
  \setlength{\itemsep}{0pt}%
}

@@

@@

\author[add]{Gökhan Göktürk}
\ead{gokhan.gokturk@sabanciuniv.edu}

\author[add]{Kamer Kaya}
\ead{kaya@sabanciuniv.edu}

@@

@@

\begin{figure}[!ht] 
    \centering
  \subfloat[\small{IC}\label{fig:ic}]{%
       \includegraphics[width=0.4\linewidth]{images/ic.pdf}}
  \subfloat[\small{WC}\label{fig:wc}]{%
        \includegraphics[width=0.4\linewidth]{images/wc.pdf}}
    \\% IMAGES HERE
  \caption{\small{\protect\subref{fig:ic} 
The directed graph $G = (V, E)$ for IC with independent diffusion probabilities. 
\protect\subref{fig:wc}
The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma^-_G(v)|$ for each vertex $v \in V$.% \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.} 
  }}
  %\label{fig_ic_model} 
  \label{fig:xx} 
\end{figure}
% \FloatBarrier
% \begin{itemize}[leftmargin=*]
% \item The {\bf Independent Cascade} model \fixme{works in rounds and activates} a vertex $v$ in the current round if one of $v$'s \fixme{incoming edges $(u, v)$ is used during the diffusion} round, \fixme{which happens with the activation probability $w_{u, v}$, given that $u$ has already been} influenced \fixme{in the previous rounds. The activation probabilities are independent (from each other and previous activations)} in the {\em independent cascade} model, which we focus on in this paper. A toy graph with activation probabilities on the edges is shown in Figure~\ref{fig:ic}.
% In theory, there can exist parallel and independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing.
